Extended Data

### 2022-03-11 doc/manuscript/Dow_manuscript_Nature.Rmd
work on discussion

<!--on the fate of extra C-->
Our results add to a growing body of evidence for a sink limitation of stem growth and $ANPP_{woody}$[@refs], wherein global change factors such as warming spring temperatures[@refs] or elevated CO~2~[@refs] enhance GPP, but woody growth is less responsive, if at all[@refs].
The fate of any additional C fixed during years with warm springs remains unresolved, but possible *destinations* -- including respiration, NSC storage, and production of foliage, reproductive structures, roots[@zohner_how_2021], or root exudates -- generally have shorter residence times that woody growth.
Indeed, in a situation where GPP was enhanced (through experimental elevation of CO~2~) but $ANPP_{woody}$ was constrained *(presumably by sink factors)*, additional C was released back to the atmosphere on relatively short time scales through enhanced respiration[@jiang_fate_2020].
Indeed, it has been observed that C loss through fall or winter respiration can offset gains from an earlier spring[@oishi_warmer_2018;@buermann_widespread_2018].
It is also possible that a buildup of NSCs that are not required for growth or other functions would feed back to reduce the rate of photosynthesis[@refs], such that sink limitation of $ANPP_{woody}$ reduces GPP relative to its potential in years with warm springs.
Either way, our results demonstrate that warm springs do not increase $ANPP_{woody}$ on an interannual time scale.

<!--.short vs long-term effects-->
It is possible that

*notes:*

- we show lack of effect on interannual scale 
- feedbacks such as greater nutrient acquisition could change this.

*old content:*

However, C allocated to nonstructural carbohydrates or relatively short-lived plant tissues would typically remain in the ecosystem beyond the end of the year[@trumbore_quantifying_2002], such that the long-term effect of warm springs on the forest C balance would not be captured in analyses of interannual variation[@zhou_explaining_2016;@fu_maximum_2019;@keenan_net_2014].
Studies within or including the temperate deciduous biome that examined long-term trends in growing season length and ecosystem C uptake[@keeling_increased_1996;@dragoni_evidence_2011;@keenan_net_2014;@finzi_carbon_2020] -- as opposed to their interannual variation -- showed increasing trends in both variables, suggesting that the C not allocated to woody productivity within the current year has a multi-year residence time within the ecosystem.

Thus, a distinction between interannual variation and directional change may be critical when considering how directional climate change is likely to affect tree growth and ecosystem C dynamics. 
As discussed above, temporal lags between C uptake and release imply that the full effects of warm spring temperatures on forest woody productivity and C cycling are unlikely to be apparent in analyses of interannual variation (including this analysis)[@kannenberg_linking_2019].
Moreover, acclimation of trees to warming temperatures[@gessler_way_2020] and, on longer time scales, species adaptations and shifts in community composition[@fisichelli_temperate_2014] are likely to alter the seasonality of forest C cycling.
If we look across spatial gradients where the latter have had time to play out, we see that warmer spring temperatures are associated with earlier leaf-out[@delgado_differences_2020] and longer growing seasons, which in turn are correlated with greater tree growth[@anderson-teixeira_joint_2021], woody productivity[@banburymorgan_global_2021], and NEE[@churkina_spatial_2005].
Thus, warming spring temperatures are expected to increase the biophysical potential for annual tree growth, but that potential is not being realized on an interannual time frame.

>>>>

<!--on the fate of extra C-->
Our results add to a growing body of evidence for a sink limitation of stem growth and $ANPP_{woody}$[@refs], wherein global change factors such as warming spring temperatures[@refs] or elevated CO~2~[@refs] enhance GPP, but woody growth is less responsive, if at all[@refs].
The fate of any additional C fixed during years with warm springs remains unresolved, but possible *destinations* -- including respiration, NSC storage, and production of foliage, reproductive structures, roots[@zohner_how_2021], or root exudates -- generally have shorter residence times that woody growth.
Indeed, in a situation where GPP was enhanced (through experimental elevation of CO~2~) but $ANPP_{woody}$ was constrained *(presumably by sink factors)*, additional C was released back to the atmosphere on relatively short time scales through enhanced respiration[@jiang_fate_2020].
Indeed, it has been observed that C loss through fall or winter respiration can offset gains from an earlier spring[@oishi_warmer_2018;@buermann_widespread_2018].
It is also possible that a buildup of NSCs that are not required for growth or other functions would feed back to reduce the rate of photosynthesis[@refs], such that sink limitation of $ANPP_{woody}$ reduces GPP relative to its potential in years with warm springs.
Either way, our results demonstrate that warm springs do not increase $ANPP_{woody}$ on an interannual time scale, contrasting with their tendency to augment _NEE_[@zhou_explaining_2016;@fu_maximum_2019;@keenan_net_2014].

<!--.short vs long-term effects-->
It is possible that, as spring warming continues, forests will adjust to directional changes in growing season length with an enhancement of $ANPP_{woody}$.
Across spatial gradients in spring temperature, warmer spring temperatures are associated with earlier leaf-out[@delgado_differences_2020] and longer growing seasons, which in turn are correlated with greater tree growth[@anderson-teixeira_joint_2021], woody productivity[@banburymorgan_global_2021], and NEE[@churkina_spatial_2005].
Thus, warming spring temperatures are likely to increase the biophysical potential for annual tree growth, but that potential is not currently being realized on an interannual time frame.
If extra photosynthate made available through a growing difference between GPP and $ANPP_{woody}$ is allocated to functions that relieve limitations on woody growth -- for example, by enhancing nutrient and water acquisition through enhanced allocation to roots[@zohner_how_2021] -- it is possible that warming spring temperatures could ultimately increase $ANPP_{woody}$ through indirect mechanisms.
Therefore, understanding how warming spring temperatures are influencing C allocation within temperate deciduous forest ecosystems remains an important outstanding question.
